The Legacy of the European Post-Master in Urbanism at TU Delft: A Text Mining Approach

### 2023-02-21 analysis/paper/paper.qmd
Increase dot size on map if multiple theses in the same location

# Show thesis locations on world map
world <- map_data("world")
ggplot() +
  geom_map(
    data = world, map = world,
    aes(long, lat, map_id = region),
    color = "black", fill = "lightgray", size = 0.1
  ) +
  geom_point(data = emu_theses, aes(longitude, latitude), color = "red") +
  coord_fixed() +
  theme_void()
```

>>>>

# Show thesis locations on world map
world <- map_data("world")
ggplot() +
  geom_map(
    data = world, map = world,
    aes(long, lat, map_id = region),
    color = "black", fill = "lightgray", size = 0.1
  ) +
  geom_count(data = emu_theses, aes(longitude, latitude), color = "red", alpha = 0.7) +
  scale_size_area(max_size = 3) +
  coord_fixed() +
  theme_void()
```
